% TeX root = ../main.tex

\chapter{Prelimnaries}

\section{Primer on Fourier Series}\label{Fourier}

\subsection{Fourier Series}

\defn{$\bbS$}{Denote $\bbS$ as the space of all complex valued $\bbZ$ periodic functions on $\bbR$ that are Lebesgue Measurable (For the applications, we take them to be \emph{continuous}). If $f\in \bbS$, then $\forall \ x \in \bbR,\ f(x)=f(x+1)$}
\defn{Hermitian Inner Product}{On $\bbS $ (Which is a vector space), define $\langle f,g\rangle:=\int_0^1 f \bar{g} dx$ } 
\defn{Fourier Coefficients $c_n$ and the Fourier Series}{For $n\in \bbZ$ $$c_n(f):=\langle f,\exp(2\pi i n x)\rangle=\int_{0}^{1} f \exp(-2\pi i n x)dx $$
The Fourier Series of the function $f$ is defined as $$\sum_{-\infty}^{\infty} c_n \exp(2\pi i n x) =\sum_{n=-\infty}^{\infty}(\int_{0}^1 f(t)\exp(-2\pi i n t)dt)(\exp(2\pi i n x))  $$}

\begin{lemma}\label{nice lemma}
{Let $f:\bbR \to \bbC$ be a $\bbZ$ periodic function. Let $c_n:=\langle f,\exp(2\pi i n x)\rangle$ as usual. Call $f$ "nice" if $\{c_n\}$ converges abosolutely, $|c_n|\leq C/n^2$ for some constant $C$ and for some $e>1/2$, for all $x\in \bbR,h\in \bbR^+$, $$|f(x+h)-f(x)|\leq C|h|^e $$ (e=1 is called \emph{Lipshitz}).
\\ If $f$ is "nice" and $c_n(f)=\langle f(x),\exp(2\pi i n x)\rangle=0$ for all $n \in \bbN$, then $f\equiv 0$.}  
\end{lemma}
\begin{lemma}
  If $f:\bbR \to \bbC$ (a $\bbZ$ periodic function) is "nice" (as defined in \ref{nice lemma}), then $$ \sum_{n \in \bbZ} c_n \exp(2\pi i n x) =f(x)$$  
\end{lemma}
\lemp{(Parseval)}{Suppose $f:\bbR\to \bbC$ is a "nice" function (as defined in \ref{nice lemma}). Then $$\langle f,f\rangle=\sum_{n\in \bbZ}|c_n|^2$$}{$\langle f,f\rangle=\int_{0}^1 (\sum_{n\in \bbZ}c_n \exp(2\pi i n x))(\sum_{m\in \bbZ}c_m\exp(-2\pi m x))dx$ which gives $$\sum_n \sum_n c_n c_m \int_0^1 (\exp(2\pi i x (n-m))dx) $$ which yields $$\sum_n \sum_m c_n c_m \delta_{mn}=\sum_n |c_n|^2$$}

\subsection{(General Discussion) Periodic Functions of a Real Variable}
Let $f:\bbR \to \bbC$ be $1-$periodic, i.e. $f(x+1)=f(x)$. This lifts to a unique function $\tilde{f}:S^1\to \bbC$.

\subsubsection{Constructing periodic functions}
Let $g:\bbR \to \bbC$, and suppose $g$ decays sufficiently fast at $\infty$. 
Let $$f(x):=\sum_{n\in \bbZ} g(x+n)$$
This function can be easily checked to be $1$ periodic. 

\subsubsection{Unfolding Trick, and Poisson Summation Formula}
We have the simple fact $$\int_{-\infty}^{\infty}g(x)dx=\sum_{n\in \bbZ} \int_{0}^1 g(x+n)dx $$
If $f$ is periodic and is generated by $g$, then $f(x)=\sum_{n\in \bbZ} g(x+n)$ and $$\int_{0}^1 f= \int_{-\infty}^{\infty} g $$
\textbf{Fourier Coefficients of $f$:}
\\ $$f_m=\int_{0}^{1}f(x)e^{-2\pi i m x} dx = \int_0^1 (\sum_{n\in \bbZ}g(x+n))e^{-2\pi i m x} dx $$
$$=\sum_{n \in \bbZ} \int_0^1 g(x+n)e^{-2\pi i m (x+n-n) }dx=\sum_{n\in \bbZ} \int_0^1 g(x+n)e^{-2\pi i m(x+n)}e^{2\pi i m n} dx$$
$$=(\text{ since }e^{2\pi i mn}=1)\sum_{n\in \bbZ} \int_0^1 g(x+n)e^{-2\pi i m(x+n)}dx=\int_{-\infty}^{\infty} g(u)e^{-2\pi i m u} du  $$
We thus have: $$f_m=\hat g(m) $$ where $\hat g $ denotes the Fourier transform of $g$.
\begin{center}\boxed{f(x)=\sum_{n\in Z}g(x+n)=\sum_{m\in \bbZ} \hat g(m) e^{2\pi i m x}}\end{center}
In the above equation, plugging $x=0$ gives us the famed \emph{\textbf{Poisson Summation Formula}:} 
\begin{theorem}\textbf{(Poisson Summation)}\\{$$\label{Poisson Summation Formula}\sum_{n \in \bbZ}g(n)=\sum_{m\in \bbZ}\hat g(m) $$
}\end{theorem}


\thmp{(Basis for $L^2(S^1)$)}{$e^{2\pi i n x}$ are periodic with period $1$ and they form a basis for $L^2(S^1)$. Moreover: 
\begin{enumerate}
  \item $$\int_{0}^{1} e^{2\pi i n x} e^{-2\pi i m x} =\delta_{nm}$$
  \item $$\sum_{\bbZ} e^{2\pi i m (x-y)}=\sum_{\bbZ}e^{2\pi i mx}e^{-2\pi i n x}=\sum_{m\in \bbZ} \delta(x-y+m)$$ (Where $\delta(x-y)$ denotes the Dirac delta centered at $y$.)
\end{enumerate}}{We prove (2): Note that if $x=y$, we get $\infty$ in the LHS, and $\sum_m\delta(m)=\delta(0)=\infty$. If $x \neq y$, We apply the unfolding trick: 
Let $f(x-y)=\sum_{n\in \bbZ} \delta(x-y+n) $ (a periodic function).
$$f(\theta)=\sum_m f_m e^{2\pi i m \theta}$$ where $$f_m=\int_{0}^{1} (\sum_{n\in \bbZ}\delta(\theta+n))e^{-2\pi i m \theta}d\theta$$
$$ =\sum_{n\in \bbZ} \int_0^1 \delta(\theta+n)e^{-2\pi im(\theta+n)}d\theta \text{ (since }e^{-2\pi i m x}\text{ is periodic)}$$
$$=\int_{-\infty}^{\infty} \delta(\theta)e^{-2\pi i m \theta} d\theta=1$$ Hence, we see that the Fourier Coefficients of our $f$ (defined using sum of $\delta$) are $1$. Hence $$\sum_{n\in \bbZ} \delta(x-y+n)=\sum_{m\in \bbZ} f_m e^{-2\pi i m (x-y)}=\sum_{m\in \bbZ} e^{-2\pi i m (x-y)}$$ Which was what we set out to prove. 
}

\subsubsection{Cauchy's Theorem}
\begin{theorem}
  (\textbf{Cauchy- weak version}) Let $f:U\to \bbC$ be holomorphic on the simply connected domain $U$. Let $P$ be some polygon on $U$. Then $$\int_P f(z)dz=0$$ 
\end{theorem}
\section{Modular Forms}
\subsection{Basic Definitions and Results}
\defn{Upper Half Plane $\bbH$}{$$\bbH:=\{z\in \bbC: im(z)>0\}$$}
\defn{$SL(2,\bbR)$}{$$SL(2,\bbR):=\bigg\{M=\bigg{(}\begin{matrix}a & b \\ c &d \end{matrix}\bigg{)}: a,b,c,d \in \bbR \textbf{ and } ad-bc=1 \bigg\} $$}
\defn{$GL(2,\bbR)$}{$$GL(2,\bbR):=\bigg\{M=\bigg{(}\begin{matrix}a & b \\ c &d \end{matrix}\bigg{)}: a,b,c,d \in \bbR \textbf{ and } ad-bc\neq 0 \bigg\} $$}
\defn{$GL^+(2,\bbR)$}{$$GL^+(2,\bbR):=\bigg\{M=\bigg{(}\begin{matrix}a & b \\ c &d \end{matrix}\bigg{)}: a,b,c,d \in \bbR \textbf{ and } ad-bc>0\bigg\} $$}
We have rather trivially the following inclusions
$$SL(2,\bbR)\hookrightarrow GL^+(2,\bbR) \hookrightarrow GL(2,\bbR) $$
\defn{Modular Form (for $SL_2(\bbZ)$)}{Let $k \in \bbZ$. $f:\bbH\to \bbC$ is a modular form of weight $k$ if: 
\begin{enumerate}
  \item For all $\bigg(\begin{matrix}a&b \\c&d \end{matrix}\bigg) \in SL(2,\bbZ)$ and $z \in \bbH$, $$f(\frac{az+b}{cz+d})=(cz+d)^k f(z) $$
  \item $f(z)$ is bounded as $im(z)\to \infty$
  \item $f$ is Holomorphic on all of $\bbH$
\end{enumerate}}
\corp{$\forall x \in \bbH \ f(x+1)=f(x)$}{Since $\bigg(\begin{matrix}1&1 \\0&1 \end{matrix}\bigg)\in SL(2,\bbZ)$, we have the result trivially.}
\corp{$\forall x \in \bbH \ f(-1/x)=x^kf(x) $}{Since $\bigg(\begin{matrix}0&-1 \\1&0 \end{matrix}\bigg)\in SL(2,\bbZ)$, we have the result.}
\corp{$f(x)=(-1)^k f(x)$}{Since $\bigg(\begin{matrix}-1&0 \\0&-1 \end{matrix}\bigg)\in SL(2,\bbZ)$, the result holds. Moreover, if $k$ is odd, $f$ has to be the 0 map. \emph{\textbf{The only non zero modular forms are of even weights.}} }
\fact\label{fact of generation of SL}{$SL(2,\bbZ)$ is generated by $\bigg(\begin{matrix}1&1 \\0&1 \end{matrix}\bigg) $ and $ \bigg(\begin{matrix}0&-1 \\1&0 \end{matrix}\bigg) $. }

\begin{corollary}
  From \ref{fact of generation of SL} we have that any modular form can be re-characterised (without reference to $SL(2,\bbZ)$) by the following axioms: $f:\bbH\to \bbC$ is a Modular Form of weight $k$ if:
  \begin{enumerate}
    \item $f$ is holomorphic on $\bbH$
    \item $f(\tau)$ bounded as $im(\tau)\to \infty$ (bounded along the $y$ coordinate of the complex plane)
    \item $f(\tau+1)=f(\tau)$ and $f(-1/\tau)=(\tau)^k f(\tau)$ $\forall \tau \in \bbH$
  
  
  \end{enumerate}
\end{corollary}

\begin{corollary}
  Since $f$ is $\bbZ$ periodic, and holomorphic, we can fourier expand $f$, which gives $$f(x+iy)=\sum_{n \in \bbZ} a_n e^{2\pi i n (x+iy)}=\sum_{n\in \bbZ} a_n e^{2\pi i nx}e^{-2\pi n y} $$
  If $a_n$ for negative $n$ were to be non zero, we would have that $f$ is unbounded as $y\to \infty$ (since $e^{2\pi n y}$ would go unbounded). Therefore, $\forall n<0, a_n=0$. $a_0$ can be $0$, in which case $\lim_{y\to \infty} f(x+iy)=a_0=0$. If $a_0=0$, then the modular form is called a \textbf{Cusp Form}.\label{cusp form} 
\end{corollary}
\subsubsection{Weakly Holomorphic Modular Forms of weight $k$ (for $SL_2(\bbZ)$)}
\defn{Weakly Holomorphic Modular Forms of weight $k$}{We say a function $f:\bbH\to \bbC$ is a weakly holomorphic modular form of weight $k$ if:
\begin{enumerate}
  \item $f(a\tau+b/c\tau+d)=(c\tau+d)^kf(\tau)$ for every $\bigg(\begin{matrix}a&b \\c&d \end{matrix}\bigg)\in SL(2,\bbZ)$
  \item $f(\tau)\in \mathcal{O}(q^{-N})$ instead of $\mathcal{O}(q^0)$ (for $f=\sum_{n \in \bbZ} a_n q^n$) which yields $f=\sum_{n=-N}^{\infty}a_n q^n $ (Note that $f$ loses the boundedness property as $im(x)$ goes to infinity. )
\end{enumerate} }

\defn{$M_k$}{Space of all Modular Forms of weight $k$ (Forms a vector space over $\bbC$).}
\defn{$S_k$}{Space of all Cusp forms ($a_0=0$, i.e. $f(x+iy)\to 0$ as $y\to \infty$) (Forms a vector space over $\bbC$).}
\defn{$M_k^!$}{Space of all weakly holomorphic forms (Forms a vector space over $\bbC$).}
\fact{$$S_k\subset M_k \subset M_k^! $$}
\begin{remark}
  Note, it is more prudent to specify the group for which we are discussing these Modular Forms, for eg. $S_k(SL_2(\bbZ))$ or $M_k(SL_2(\bbZ))$ (for reasons that will be clear later).
\end{remark}
\subsubsection{Some Growth Properties of Modular forms ($SL_2(\bbZ)$)}
\begin{enumerate}
  \item For $f\in S_k(SL_2(\bbZ))$, $a_n\in \mathscr{O}(n^{k/2})$  
  \item For $f \in M_k(SL_2(\bbZ)), a_n \in \mathscr{O}(n^{k-1})$
  \item For $f \in M_k^!(L_2(\bbZ)), a_n \in \mathscr{O}(e^{C\sqrt n})$
\end{enumerate}
\defn{Eisenstein Series $E_k$}{$$E_k(z):=\sum_{(m,n)\in \bbZ^2, (m,n)\neq 0}\frac{1}{(mz+n)^k}$$}
\begin{remark}
  $E_k(z)$ is a modular form of weight $k$ (for $SL_2(\bbZ)$) for all $k\geq 4$. They are very important examples of modular forms for they, in some sense, form the "building blocks" to construct other modular forms.

\end{remark}
\defn{Discriminant function $\Delta$}{ $$\Delta(z):= q \Pi_1^{\infty} (1-q^n)^{24} $$ (Where $q=e^{2\pi i z}$). This function is a \emph{cusp form} of weight 12.}
We present, without proof, one of the cornerstone theorems in Modular Forms theory:
\begin{theorem}\label{mk vs mk-12}
\begin{enumerate}
  \item $M_k(SL_2(\bbZ))$ is generated by the monomials $E_4^{\alpha}E_6^{\beta}$ such that $4\alpha+6\beta=k$. In other words, as a vector space we see that $$M_k(SL_2(\bbZ))=\langle\{E_4^{\alpha}E_6^{\beta}:4\alpha+6\beta=k \ (\text{ in integers}) \} \rangle$$ A trivial corollary of this is that, $M_k(SL_2(\bbZ))$ is a finite dimensioned vector space.
  \item $$M_*(SL_2(\bbZ))=\oplus_k M_k(SL_2(\bbZ))$$ forms a \emph{Graded Algebra-} A direct sum of submodules that forms an algebra. Moreover, $$M_*(SL_2(\bbZ))=\bbC[E_4,E_6]$$ This says that, in principle, the space of all modular forms for $SL_2(\bbZ)$ acts as the set of all 2 variable polynomials over $\bbC$ ($E_4$ and $E_6$ are algebraically independent). 
  \item \label{mk vs ek and sk} $$M_k(SL_2(\bbZ))=\bbC \cdot E_k+S_k$$ This result says that every modular form is some scalar times the Eisenstein, with the "error term" being a cusp form (or the other way around, where every modular form is a cusp form, with the error term being a factor of the Eisenstein)
  \item \label{sk vs mk-12}$$S_k=\Delta \cdot M_{k-12}$$
\end{enumerate}
\end{theorem}
\begin{remark}
  With the results \ref{mk vs ek and sk} and \ref{sk vs mk-12} of \ref{mk vs mk-12}, we see that $M_k=\bbC E_k+\Delta M_{k-12}=\bbC E_k+\Delta (\bbC E_{k-12}+\Delta M_{k-24})=\bbC E_k+\Delta (\bbC E_{k-12} + \Delta(\bbC E_{k-24}+\Delta M_{k-36}))=\cdots $ from which we get that any modular form $f$ of weight $k$ can be written as $$ f=\sum_{n=0}^{[k/12]}\alpha_n E_{k-12n} \Delta^n$$
\end{remark}
\subsection{Fundamental Domain and the action of $SL_2(\bbZ)$ on $\bbH $}
The defining action of a $\gamma=\begin{bmatrix}
  a \ b \\ c \ d  
\end{bmatrix} \in SL_2(Z)$ on a vector $z \in \bbH $ is given by: $$ z \mapsto \gamma z=\frac{az+b}{cz+d}$$
Note the following fact: $$\operatorname{im}(\frac{az+b}{cz+d})=\frac{(ad-bc) \operatorname{im}(z)}{|cz+d|^2} $$ (This, in some sense, necissitates the need for us to look at $GL_2^+(\bbR)$. The necessity to look at $SL_2(\bbZ)$ comes from analysing Lattices of the form $\omega_1 \bbZ \oplus \omega_2 \bbZ$ (for $\omega_1,\omega_2 \in \bbR$). A change of basis of the lattice corresponds to a $SL_2(\bbZ)$ multiplication).
\newline Since $\begin{bmatrix}
  1 \ 1 \\ 0 \ 1  
\end{bmatrix} \text{ and }\begin{bmatrix}
  0 \ -1 \\ 1 \ 0  
\end{bmatrix}  \in SL_2(\bbZ)$, the respective actions are $z \mapsto z+1$ (translations) and $z \mapsto -1/z$ (inversions). 
\defn{Fundamental Domain $\mathcal F$ for $\Gamma \leq SL_2(\bbZ)$}{A fundamental domain is a subset of $\bbH$ under the action of $\Gamma$, i.e. 
$$\bbH= \bigg.\cup_{\gamma \in \Gamma} \gamma \mathcal F $$ 
such that: \begin{enumerate}
  \item $(\gamma_1 \mathcal F)^{\circ} \cap (\gamma_2 \mathcal F)^{\circ}=\varnothing $.
  \item $(\bar{\mathcal F})^{\circ}=\mathcal F$ (The set is "full" in some sense).
  \item $\forall z \in \bbH$, $\exists d \in \mathcal F $ and $\gamma \in \Gamma$ such that $\gamma d=z$. 
\end{enumerate}
} 
\begin{example}
  A fundamental Domain for $SL_2(\bbZ)$ is $$\mathcal F_{SL_2(\bbZ)}:=\{x \in \bbH: |\operatorname{Re}(x)|\leq \frac{1}{2} \text{ and }|x|>1 \} $$
\end{example}

% TIKZ PICTURE %

\begin{center}
\begin{tikzpicture}[scale=2]\label{fundamental_domain}

% Axes
\draw[->] (-1.5,0) -- (1.5,0) node[right] {$\Re(\tau)$};
\draw[->] (0,-0.1) -- (0,2.0) node[above] {$\Im(\tau)$};

% Shaded fundamental domain
\fill[red!30, opacity=0.6]
  (-0.5, 1.8)
  -- (-0.5, 0.866)
  arc[start angle=120, end angle=60, radius=1]
  -- (0.5, 1.8)
  -- cycle;

% Boundary lines Re(tau) = ±1/2, drawn only from arc upward
\draw[thick] (-0.5, 0.866) -- (-0.5, 1.8);
\draw[thick] ( 0.5, 0.866) -- ( 0.5, 1.8);

% Unit circle arc from 120° to 60°
\draw[thick] (-0.5, 0.866) arc[start angle=120, end angle=60, radius=1];

% Dashed extensions below the domain (for context)
\draw[dashed, gray] (-0.5, 0) -- (-0.5, 0.866);
\draw[dashed, gray] ( 0.5, 0) -- ( 0.5, 0.866);
\draw[dashed, gray] (-0.5, 0.866) arc[start angle=120, end angle=180, radius=1];
\draw[dashed, gray] ( 0.5, 0.866) arc[start angle=60,  end angle=0,   radius=1];

% Tick marks and labels on x-axis
\draw (-0.5, 0.03) -- (-0.5,-0.03) node[below] {$-\tfrac{1}{2}$};
\draw ( 0.5, 0.03) -- ( 0.5,-0.03) node[below] {$\tfrac{1}{2}$};
\draw ( 1.0, 0.03) -- ( 1.0,-0.03) node[below] {$1$};
\draw (-1.0, 0.03) -- (-1.0,-0.03) node[below] {$-1$};

% Special points
\fill (0, 1) circle (1pt) node[right] {$i$};
\fill ({cos(60)}, {sin(60)}) circle (1pt) node[above right] {$e^{i\pi/3}$};
\fill ({cos(120)}, {sin(120)}) circle (1pt) node[above left] {$e^{2i\pi/3}$};

% Label
\node at (0, 1.35) {$\mathcal{F}$};

\end{tikzpicture}
\end{center}

%TIKZ PICTURE ENDS

\subsubsection{Shimura's Slash Notation}
\defn{$f(z)|_k[\gamma]$}{Let $\gamma \in GL_2^+(\bbQ)$
Define $$f(z)|_k[\gamma]:=(\operatorname{det}(\gamma))^{k/2} j(\gamma,z)f(\gamma z) $$
Where $\gamma z:= \frac{az+b}{cz+d}$ and $j(\gamma,z):= (cz+d)^{-k}$ (Called the Automorphy factor). Altogether the above shorthand reads:
$$f(z)|_k[\gamma]:= (\operatorname{det}(\gamma))^{k/2}(cz+d)^{-k} f\bigg{(}\frac{az+b}{cz+d}\bigg{)} $$ }
\fact{$f(z)|_k[\gamma_1 \gamma_2]=(f(z)|_k[\gamma_1])|_k[\gamma_2] $}

\begin{comment}
\subsubsection{What are Cusps?}
We first look at the map $(x,y)=z\mapsto e^{2\pi i z}=e^{2\pi i x}e^{-2\pi y}$. This maps the upper half plane to the punctured open unit disc ($y\to 0$ maps to the $|x|=1$ boundary, and $i\infty$ (which is $\infty $, specifically reached through, $\lim(y)\to \infty$)) maps to 0. $q=e^{2\pi i z}=0$ corresponds to $z=i \infty$ (the specific $\infty$ reached through $\lim y \to \infty$). Note that, the points on the boundary of the unit disc corresponds to $y \to 0$, which don't belong to the upper half plane. Hence, the image of $\bbH$ under $e^{2\pi i z}$ is not compact.

The problem is that, the upper half plane $\bbH$ is itself not compact. This can be made compact by adding a point $\infty$ and $\bbR$ and defining topologies as usual. This makes a compact Riemann Surface, but it is not the most viable choice for our goals with modular forms. 
This is where the topology $\Gamma/ \bbH$ comes into picture. Note that, 
$${SL_2(\bbZ)} / {\bbH}=\mathcal F=\{x \in \bbH: |\operatorname{Re}(x)|\leq 1/2 \text{ and }|x|>1\}$$
\end{comment}

\subsubsection{What are Cusps?}

We begin by considering the map
\[
z = x + iy \mapsto q = e^{2\pi i z} = e^{2\pi i x} e^{-2\pi y}.
\]
Since $y > 0$, we have $0 < |q| < 1$, so this map sends the upper half-plane $\bbH$ to the punctured unit disk.

As $y \to \infty$, we see that $|q| = e^{-2\pi y} \to 0$. Thus the point $z = i\infty$ corresponds to $q = 0$. On the other hand, as $y \to 0^+$, we have $|q| \to 1$, so points approach the boundary of the unit disk.

This shows that the upper half-plane $\bbH$ corresponds to a punctured disk, with the missing point $q=0$ corresponding to $z = i\infty$.

Now consider first the action of $SL_2(\bbZ)$ on $\bbH$. The quotient space $SL_2(\bbZ)\backslash \bbH$ can be visualized using a fundamental domain $\mathcal{F} \subset \bbH$, for example:
\[
\mathcal{F} = \left\{ z \in \bbH : |\operatorname{Re}(z)| \le \tfrac{1}{2}, \ |z| \ge 1 \right\}.
\]
This space, however, is non compact. In order to compactify this space, (and viably include the relevant points, i.e. those that correspond to $q=0$ and $|q|=1$)